\documentclass{letter}

\signature{Dr. habil. Prof. Anatoly Baskakov}
\address{Department of Systems Analysis and Control\\
  1 Universitetskaya\\
  Voronezh, Russia 394000}
\begin{document}
\begin{letter}{Skoltech's and HSE's admissions boards,\\
Skolkovo Institute of Science and Technology\\
Nobelya Ulitsa 3\\
Moscow, Russia 121205
}
\opening{A letter of recommendation for Serge Kozlukov\\[1cm]
  To Whom it may concern:}
I'm pleased to recommend Serge Kozlukov for admission to the Statistical
Learning Theory programme of Skoltech and HSE. In the past three years
he's been a student in my functional analysis course in Fall~2015--Spring~2016,
he participated in my specialized seminars,
and has been working in my research group since the May of 2016.
During these years he demonstrated an excitement both about mathematical culture
and applications. He's always open for new problems. He's comfortable with
jumping right into new unfamiliar topics, making, acknowledging, and
fixing mistakes. His enthusiasm and ambition are sometimes indistinguishable from
naivety.

He came to me from the Mechanics department in 2015 as a mostly self-taught student
who was at that moment more interested in applied disciplines and software
development. He was seeking for a strong mathematical foundation for these
activities. Being a self-taught student he had some gaps which I watched him
rapidly fill during our work. The result of this work (aside from conference
talks and papers) are two articles in peer-reviewed journals both on the problem
of spectral estimations for perturbed operators corresponding to digraphs of
special form. That work required familiarity with basic linear algebra and
linear functional analysis, in particular the fixed-point theory. It also
required research ability, some ingenuity, and communication skills.

Serge's GPA is almost exactly $5$ on a $5.0$ scale. Thus he proved not only an
able researcher but also an excellent student.

I believe he needs to keep working in the field of fundamental mathematics under
a leadership of an experienced and well \emph{cultured} mathematician to build a
strong basis for his future research. One can become a decent, or even good
mathematician, yet one will not stand out without a proper guidance and
environment --- not unless a miracle. Yet Serge's urge to immediately apply the
results of his work and see its direct impact is prevailing. The Statistical
Learning Theory programme is an opportunity for him to find a satisfaction to
both needs. With his ambition and these few skills gained in these last years,
I'm certain he's an excellent candidate for the SLT Masters program.

\closing{Yours sincerely,}
\end{letter}
\end{document}